\documentclass[a4paper,12pt]{article}
\usepackage[usenames,dvipsnames]{color}
\usepackage{mathptmx}
\usepackage[version=4]{mhchem}
\usepackage[
  a4paper,
  top = 1.70cm,
  bottom = 1.70cm,
  left = 1.70cm,
  right = 1.70cm
]{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    urlcolor=RoyalBlue,
    citecolor=RoyalBlue,
    anchorcolor=RoyalBlue
}

\urlstyle{same}
\input{glyphtounicode}
\renewcommand{\baselinestretch}{1.3}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{30pt}
\setlength{\skip\footins}{20pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\begin{document}
\begin{center}
    {\Huge \scshape {\fontsize{25}{30}\selectfont{Reza}} {\fontsize{25}{30}\selectfont{\textbf{Aliasgari Renani}}}} \\ \vspace{3pt}
    {\small \raisebox{-0.2\height}\ {17/11/2025}} $|$
    {\small \raisebox{-0.2\height}\ {Essay}} $|$
    {\small \raisebox{-0.2\height}\ {System Analysis, Control and Information Processing}} $|$
    {\small \raisebox{-0.2\height}\ {Russian Federation}} $|$
    {\small \raisebox{-0.2\height}\ {PhD}}
    \vspace{-10pt}
\end{center}
\vspace{-10pt}
\noindent\rule{\textwidth}{0.5pt}

My research objective is to advance the field of electronic engineering by developing radiation-resistant FPGA based video processors for space applications, focusing on optimizing image signal processing algorithms for hardware implementation. The PhD program in System Analysis, Control and Information Processing, Statistics in Russian Federation and specifically at Moscow Institute of Physics and Technology (MIPT) provides an ideal platform for me to achieve this, building directly on my previous studies and research at the university.
\vspace{10pt}

I have completed my Bachelor's degree in technical physics and Master's degree in applied mathematics and physics at MIPT, where my work on radiation effects in semiconductors and Field Programmable Gate Arrays (FPGA) development has deepened my interest in creating radiation-hardened hardware systems. I want to develop FPGA and Application-Specific Integrated Circuit (ASIC) based video processors, integrating system analysis and control techniques to enhance throughput, latency, and reliability under harsh conditions.
\vspace{10pt}

I joined Dr.\ Koveshnikov's laboratory in the Institute of Microelectronics Technology at the Russian Academy of Sciences over two years ago to study radiation effects on microelectronic structures, focusing on electrical characterization of semiconductors and \ce{SiO2}-based Metal-Oxide-Semiconductor (MOS) devices. We studied the impact of electron and gamma irradiation and hydrogen plasma treatment on MOS devices, identified traps by location (oxide, semiconductor, interface) and carrier type (electrons, holes). This work has resulted in a first author publication\footnotemark[1] and provides insight into device stability under bias stress, radiation immunity, and oxide trap density at the dielectric-semiconductor interface. I also developed optimized MATLAB applications to automate the experimental characterization techniques, which reduced run times and created measurement pipelines. Beyond deepening my understanding of semiconductor physics, this research also gave me invaluable experience handling experimental equipment and automating experimental techniques using MATLAB and Python.
\vspace{10pt}

After my undergraduate degree, I joined the System on Chip Development Laboratory (Design center for the development of microprocessor technology for AI systems) and the Laboratory of Plasma Systems under the supervision of Dr.\ Vasiliev and Dr.\ Chesnokov to develop FPGA-based systems and to study radiation and plasma effects on these structures. I implemented video processing algorithms by manual Verilog coding and by generating HDL from Simulink models. I verified functionality of the algorithms using testbenches and Python automation scripts. In the Plasma Lab, we ran experiments where an FPGA with an attached camera and a synthesized image processing design was placed in an electron beam plasma system with low pressure oxygen and exposed to electron irradiation and X-rays generated from a tungsten target. The FPGA output signal was monitored while thermal cycling was applied and preliminary functionality tests were performed.
\vspace{10pt}

\newpage

In the System on Chip Development Laboratory, which operates under the company YADRO, I ported mathematical algorithms into efficient Verilog implementations, built a fixed-point library, and created LUT-based function approximations using Horner’s method to support fixed-point computations. I implemented a range of image processing algorithms, including rgb2hsv conversion, color segmentation, Sobel edge detection, global tone mapping, demosaicing, bird’s eye view transformation, fisheye correction, and image resizer, through both Simulink HDL code generation and manually written Verilog. I optimized these for latency and throughput, addressing synchronization and pipelining challenges. 
\vspace{10pt}

For verification, I developed comprehensive testbenches in Verilog and employed Python for simulation automation and data analysis to confirm DSP functionality and performance. I then synthesized, mapped, and routed the HDL code using Vivado on Xilinx Zybo Z7 boards, verifying the ISP algorithms first by streaming test images via HDMI from a host computer and later with a live camera connected directly to the FPGA. This hands on experience in hardware implementation and testing has strengthened my collaboration with YADRO.

\vspace{10pt}
My experience with irradiated semiconductors, plasma systems, and FPGA design has inspired me to pursue PhD studies at MIPT in System Analysis, Control and Information Processing, Statistics. I plan to investigate radiation effects on FPGA devices, identifying impacts on components like RAMs and MOSFETs, and design more resistant architectures such as replacing SRAM with ReRAM to improve tolerance in space environments. This aligns with my ongoing work in the Design Center for the Development of Microprocessor Technology for AI Systems and the System on Chip Development Laboratory at MIPT, where I can continue optimizing ISP algorithms for video processors. My work on generating HDL code for video-processing algorithms is forthcoming and will be presented\footnotemark[2] at the FPGA-Systems 2025 Conference in Moscow. I look forward to continuing my research in Russia to deploy these systems for real-time signal processing in aerospace applications.
\vspace{10pt}

As an international student already integrated into MIPT's research community, including collaboration with the Institute of Microelectronics Technology, Russian Academy of Sciences, I am well prepared to contribute to and benefit from its collaborative environment. I am motivated by projects that combine experimental testing with hardware optimization, and I look forward to applying my skills in Verilog and radiation analysis to advance FPGA-based video processors, potentially supporting Russia's space initiatives. It would be a privilege to continue my education at MIPT in Russia, a center of scientific innovation with a strong emphasis on practical engineering solutions.

\footnotetext[1]{R. Aliasgari Renani, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov, Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by capacitance-voltage and thermally stimulated current techniques, Russian Microelectronics, 2023}
\footnotetext[2]{V. Vologin, R. Aliasgari Renani, V. Vasilevskiy, V. Chesnokov, Comparative analysis of manual Verilog and Simulink-generated HDL code for image processing algorithms. Presentation, \href{https://meetups.yadro.com/fpga-msk-1125/}{YADRO FPGA-Systems Conference 2025}}

\end{document}