
\documentclass[a4paper,12pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[version=4]{mhchem}
\usepackage[dvipsnames]{xcolor}
\usepackage[backend=biber,style=ieee]{biblatex}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{footmisc}
\usepackage{csquotes}
\usepackage{fontawesome5}
\usepackage[
  a4paper,
  top        = 2.00cm,
  bottom     = 2.00cm,
  left       = 2.00cm,
  right      = 2.00cm,
  headheight = 15pt,
  headsep    = 5pt,
  footskip   = 15pt
]{geometry}

\newcommand{\degreeawardvalue}{}
\newcommand{\universityvalue}{}
\newcommand{\addressvalue}{}
\newcommand{\unilogovalue}{}
\newcommand{\copyyearvalue}{}
\newcommand{\defenddatevalue}{}
\newcommand{\orcidvalue}{}
\newcommand{\rightsstatementvalue}{}
\newcommand{\degreeaward}[1]{\def\degreeawardvalue{#1}}
\newcommand{\university}[1]{\def\universityvalue{#1}}
\newcommand{\address}[1]{\def\addressvalue{#1}}
\newcommand{\unilogo}[1]{\def\unilogovalue{#1}}
\newcommand{\copyyear}[1]{\def\copyyearvalue{#1}}
\newcommand{\defenddate}[1]{\def\defenddatevalue{#1}}
\newcommand{\orcid}[1]{\def\orcidvalue{#1}}
\newcommand{\rightsstatement}[1]{\def\rightsstatementvalue{#1}}
\newcommand{\titleskip}{\vskip 4\bigskipamount}
\newcommand{\authorskip}{\vskip 2\bigskipamount}
\newcommand{\resumesection}[2]{\section{\textcolor{red}{#1}#2}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeItem}[1]{
    \item\small{#1}
}
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \small#3 & \small #4
    \end{tabular*}
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsecpresnum}{Chapter~}
\renewcommand{\cftsecaftersnum}{:}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\thepage}
\urlstyle{same}
\addbibresource{references.bib}
\hypersetup{
  colorlinks=true,
  linkcolor=RoyalBlue,
  urlcolor=RoyalBlue,
  citecolor=RoyalBlue,
  anchorcolor=RoyalBlue
}
\settowidth{\cftsecnumwidth}{Chapter 9: }
\titleformat{\section}
  {\normalfont\Large\bfseries}
  {Chapter \thesection:}
  {0.5em}
  {}
% \titleformat{\section}{
%     \scshape\raggedright\large\bfseries
%     }{}{0em}{}[\color{black}\titlerule]
%     \titlespacing{\section}{0pt}{5pt}{5pt}

\setstretch{1.5}
\setlist[itemize]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlist[enumerate]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlength{\footnotesep}{15pt} 
\setlength{\skip\footins}{15pt} 
\setlength{\parskip}{5pt}

\begin{document}

{\centering
  {\scshape \textls[50]{\fontsize{25}{30}\selectfont Reza {\bfseries Aliasgari Renani}}} \\ 
  {\fontsize{10}{10}\selectfont 11/01/2026} $|$
  {\fontsize{10}{10}\selectfont Motivation Letter} $|$
  {\fontsize{10}{10}\selectfont Tallinn University of Technology} $|$
  {\fontsize{10}{10}\selectfont PhD (E-Sailors 10)} $|$
  {\fontsize{10}{10}\selectfont Lunar Orbit Communications}
\par}
\vspace{-15pt}
\noindent\rule{\textwidth}{0.5pt}

\vspace{-5pt}

My research objective is to contribute to lunar-orbit communications and RF ranging for ESTCube-LuNa by designing and validating the space-segment communication and ranging systems. The E-Sailor~10 doctoral position at Tallinn University of Technology focuses on defining requirements and preliminary designs for onboard communications under E-sail rotation constraints, as well as preparing the space-segment RF ranging experiment in close collaboration with E-Sailor~9. This focus matches my background in experimental systems, signal processing, and mission-relevant hardware testing. I am completing the final year of my Master's degree in Plasma Physics at Moscow Institute of Physics and Technology, and my experience with measurement systems and FPGA-based instrumentation has led me to pursue doctoral research in space communications and ranging.

I joined Dr.\ Koveshnikov's laboratory in the Russian Academy of Sciences over two years ago to study irradiated semiconductor devices. We investigated the effects of electron and gamma irradiation and hydrogen plasma treatments on \ce{SiO2}-based MOS devices, distinguishing trap contributions by location (oxide, semiconductor, interface) and carrier type (electrons, holes) using electrical characterization techniques. This work resulted in a first-author publication\footnote{R.~Aliasgari~Renani, O.A.~Soltanovich, M.A.~Knyazev, S.V.~Koveshnikov, ``Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by C--V and TSC techniques,'' \textit{Russian Microelectronics}, 2023, DOI: \href{https://doi.org/10.1134/S1063739723600516}{10.1134/S1063739723600516}} and strengthened my understanding of device stability under bias stress and radiation. I also developed optimized MATLAB automation programs for experimental techniques such as TSC, C--V, I--V, I--T, and DLTS measurements, enabling systematic data acquisition and reducing experimental run-times.

After my undergraduate degree, I joined the System-on-Chip Development Laboratory under the supervision of Dr.\ Vasiliev to develop FPGA-based systems. I implemented video-processing algorithms in Verilog using both manual coding and HDL generated from Simulink models, built verification testbenches, and used Python for quality control. I developed a fixed-point arithmetic library and LUT-based function approximations using Horner's method. I evaluated resource utilization (LUTs and BRAM) and synthesized the designs on a Xilinx Zybo Z7 board with live camera input and HDMI output. The codebase was maintained under Git-based source control. Concurrently, at the Laboratory of Plasma Systems, I conducted research on radiation and plasma effects on FPGA devices. We exposed an FPGA board to 25--60~keV electron beams in low-pressure oxygen, generating plasma and X-rays from a tungsten target while applying thermal cycling. The FPGA output signal was continuously monitored, and preliminary functionality tests were performed during and after exposure.

I have also worked on engineering projects\footnote{Project repositories: \href{https://github.com/icarus-imperium/rocket-2025}{Model Rocket (Icarus Imperium)}, \href{https://github.com/rezaaliasgarirenani/Rover}{Model Lunar Rover}, \href{https://github.com/rezaaliasgarirenani/Aircraft-Detection-System}{Aircraft Detection System}, \href{https://github.com/rezaaliasgarirenani/Non-Conservative-Electric-Fields-and-Voltmeters}{Non-Conservative Electric Fields and Voltmeters}} both independently and in team settings. In group projects, I built model rockets (40 and 60~N$\cdot$s impulse) and completed multiple launches, and I collaborated on a model lunar rover through several prototypes. I developed an aircraft detection system using photoresistors and transistor circuits with rotational and translational tracking. In an individual electronics experiment on non-conservative electric fields, I designed the setup, collected data, and documented how voltmeter readings become path-dependent under a time-varying magnetic flux. I also designed a CubeSat deployer and vibration fixture and validated prototypes through vibration testing.

In E-Sailor~10, I want to turn the project goals into a concrete space-segment design and figure out the requirements and specifications for the onboard communications system, a workable RF-ranging experiment, and validation tests in the EMC chamber and outdoors. I also want to build the data-processing workflows for comparing pre- and post-experiment orbit determinations and for quantifying E-sail thrust from the ranging data. I will document the work carefully and share results through reports, publications, and E-Sailors workshops.

This position continues the line of work I have followed so far with experimental hardware, signal processing, and measurement systems that must perform in real mission conditions. I would like to pursue this research under the supervision of Prof.\ Ivo M\"uursepp at TalTech and collaborate closely with the E-Sailors team. The mix of TalTech's communications expertise and the E-Sailors infrastructure is an environment where I can grow into careful, mission-focused engineering work.


\end{document}
