
\documentclass[a4paper,12pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[version=4]{mhchem}
\usepackage[dvipsnames]{xcolor}
\usepackage[backend=biber,style=ieee]{biblatex}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{footmisc}
\usepackage{csquotes}
\usepackage{fontawesome5}
\usepackage[
  a4paper,
  top        = 2.00cm,
  bottom     = 2.00cm,
  left       = 2.00cm,
  right      = 2.00cm,
  headheight = 15pt,
  headsep    = 5pt,
  footskip   = 15pt
]{geometry}

\newcommand{\degreeawardvalue}{}
\newcommand{\universityvalue}{}
\newcommand{\addressvalue}{}
\newcommand{\unilogovalue}{}
\newcommand{\copyyearvalue}{}
\newcommand{\defenddatevalue}{}
\newcommand{\orcidvalue}{}
\newcommand{\rightsstatementvalue}{}
\newcommand{\degreeaward}[1]{\def\degreeawardvalue{#1}}
\newcommand{\university}[1]{\def\universityvalue{#1}}
\newcommand{\address}[1]{\def\addressvalue{#1}}
\newcommand{\unilogo}[1]{\def\unilogovalue{#1}}
\newcommand{\copyyear}[1]{\def\copyyearvalue{#1}}
\newcommand{\defenddate}[1]{\def\defenddatevalue{#1}}
\newcommand{\orcid}[1]{\def\orcidvalue{#1}}
\newcommand{\rightsstatement}[1]{\def\rightsstatementvalue{#1}}
\newcommand{\titleskip}{\vskip 4\bigskipamount}
\newcommand{\authorskip}{\vskip 2\bigskipamount}
\newcommand{\resumesection}[2]{\section{\textcolor{red}{#1}#2}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeItem}[1]{
    \item\small{#1}
}
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \small#3 & \small #4
    \end{tabular*}
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsecpresnum}{Chapter~}
\renewcommand{\cftsecaftersnum}{:}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\thepage}
\urlstyle{same}
\addbibresource{references.bib}
\hypersetup{
  colorlinks=true,
  linkcolor=RoyalBlue,
  urlcolor=RoyalBlue,
  citecolor=RoyalBlue,
  anchorcolor=RoyalBlue
}
\settowidth{\cftsecnumwidth}{Chapter 9: }
\titleformat{\section}
  {\normalfont\Large\bfseries}
  {Chapter \thesection:}
  {0.5em}
  {}
% \titleformat{\section}{
%     \scshape\raggedright\large\bfseries
%     }{}{0em}{}[\color{black}\titlerule]
%     \titlespacing{\section}{0pt}{5pt}{5pt}

\setstretch{1.5}
\setlist[itemize]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlist[enumerate]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlength{\footnotesep}{15pt} 
\setlength{\skip\footins}{15pt} 
\setlength{\parskip}{5pt}

\begin{document}

{\centering
  {\scshape \textls[50]{\fontsize{25}{30}\selectfont Reza {\bfseries Aliasgari Renani}}} \\ 
  {\fontsize{10}{10}\selectfont 28/01/2026} $|$
  {\fontsize{10}{10}\selectfont Cover Letter} $|$
  {\fontsize{10}{10}\selectfont PhD} $|$
  {\fontsize{10}{10}\selectfont Semiconductor Physics} $|$
  {\fontsize{10}{10}\selectfont NS26-ESRF05} $|$
  {\fontsize{10}{10}\selectfont Rome Tre University} $|$
  {\fontsize{10}{10}\selectfont ESRF} \\
  {\fontsize{10}{10}\selectfont Nanosecond Imaging of Operating Microelectronic Devices by X-ray Diffraction Microscopy}
\par}
\vspace{-15pt}
\noindent\rule{\textwidth}{0.5pt}

\vspace{-5pt}

My research objective is to image lattice strain and heat evolution in operating microelectronic devices on sub nanosecond timescales using X-ray diffraction microscopy. The project targets strain and thermal effects that limit efficiency and lifetime in devices based on SiGe and SiGeSn heterostructures under realistic operating conditions. Beamline ID01 at the ESRF is dedicated to micro and nano beam X-ray diffraction imaging and enables advanced studies of epitaxial materials and microelectronic devices, including time resolved full field diffraction microscopy. This setting connects time domain device physics with synchrotron X-ray methods that can resolve spatial and temporal strain distributions.

I joined Dr.\ Koveshnikov's laboratory in the Russian Academy of Sciences three years ago to study irradiated semiconductor devices. We investigated the effects of electron and gamma irradiation and hydrogen plasma treatments on \ce{SiO2}-based MOS devices, identifying traps by location (insulator, semiconductor, interface) and carrier type (electrons, holes) using electrical characterization techniques. This work resulted in a first-author publication\footnote{R.~Aliasgari~Renani, O.A.~Soltanovich, M.A.~Knyazev, S.V.~Koveshnikov, ``Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by C--V and TSC techniques,'' \textit{Russian Microelectronics}, 2023, DOI: \href{https://doi.org/10.1134/S1063739723600516}{10.1134/S1063739723600516}} and strengthened my understanding of device stability under bias stress and radiation. I also developed optimized MATLAB automation programs for experimental techniques such as TSC, C--V, I--V, I--T, and DLTS measurements, which enabled systematic data acquisition and reduced experimental run-times.

After my undergraduate degree, I was interested in extending my work from basic semiconductor devices to more complex microelectronic systems and their interaction with radiation. I joined the SoC Development Laboratory to learn about programmable hardware and to work on FPGA-based systems. We implemented image signal processing (ISP) algorithms in Verilog using both manual coding and generated HDL code from Simulink models. I developed a fixed-point arithmetic library, built verification testbenches, and used Python for quality control. We evaluated resource utilization after synthesizing the designs on a Xilinx Zybo Z7 board with live camera input and HDMI output. The codebase was maintained under Git-based source control. 

Concurrently, at the Laboratory of Plasma Systems under the supervision of Dr.\ Vasiliev, we conducted research on radiation and plasma effects on FPGA devices. We exposed an FPGA board to 25--60~keV electron beams in low-pressure oxygen, generating plasma and X-rays from a tungsten target while applying thermal cycling. The FPGA output signal was continuously monitored, and preliminary functionality tests were performed during and after exposure.

Under the supervision of the ID01 team and Dr. Schülli, I will contribute to the development of sub nanosecond X-ray diffraction microscopy experiments on operating microelectronic devices. Prior work on electrically driven device response and defect related charge dynamics supports interpretation of time resolved strain signals during device operation. Experience with automated measurement control supports synchronized device biasing, data acquisition, and timing with time resolved detection at the beamline. Work with complex hardware platforms and verification workflows supports stable operation of device test benches during beamtime.

This project extends my research path from radiation induced charge dynamics to time resolved strain mapping in operating semiconductor devices. X-ray diffraction microscopy will provide quantitative links between lattice strain, heat generation, and energy dissipation, which are central to reliability and device design. The work at ESRF and Rome Tre University will produce measurement protocols and analysis methods that can transfer to semiconductor technology development. This trajectory supports my long term goal of developing diagnostics for charge, field, and strain control in advanced electronic materials.

\end{document}
