
\documentclass[a4paper,12pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[version=4]{mhchem}
\usepackage[dvipsnames]{xcolor}
\usepackage[backend=biber,style=ieee]{biblatex}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{footmisc}
\usepackage{csquotes}
\usepackage{fontawesome5}
\usepackage[
  a4paper,
  top        = 2.00cm,
  bottom     = 2.00cm,
  left       = 2.00cm,
  right      = 2.00cm,
  headheight = 15pt,
  headsep    = 5pt,
  footskip   = 15pt
]{geometry}

\newcommand{\degreeawardvalue}{}
\newcommand{\universityvalue}{}
\newcommand{\addressvalue}{}
\newcommand{\unilogovalue}{}
\newcommand{\copyyearvalue}{}
\newcommand{\defenddatevalue}{}
\newcommand{\orcidvalue}{}
\newcommand{\rightsstatementvalue}{}
\newcommand{\degreeaward}[1]{\def\degreeawardvalue{#1}}
\newcommand{\university}[1]{\def\universityvalue{#1}}
\newcommand{\address}[1]{\def\addressvalue{#1}}
\newcommand{\unilogo}[1]{\def\unilogovalue{#1}}
\newcommand{\copyyear}[1]{\def\copyyearvalue{#1}}
\newcommand{\defenddate}[1]{\def\defenddatevalue{#1}}
\newcommand{\orcid}[1]{\def\orcidvalue{#1}}
\newcommand{\rightsstatement}[1]{\def\rightsstatementvalue{#1}}
\newcommand{\titleskip}{\vskip 4\bigskipamount}
\newcommand{\authorskip}{\vskip 2\bigskipamount}
\newcommand{\resumesection}[2]{\section{\textcolor{red}{#1}#2}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeItem}[1]{
    \item\small{#1}
}
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \small#3 & \small #4
    \end{tabular*}
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsecpresnum}{Chapter~}
\renewcommand{\cftsecaftersnum}{:}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\thepage}
\urlstyle{same}
\addbibresource{references.bib}
\hypersetup{
  colorlinks=true,
  linkcolor=RoyalBlue,
  urlcolor=RoyalBlue,
  citecolor=RoyalBlue,
  anchorcolor=RoyalBlue
}
\settowidth{\cftsecnumwidth}{Chapter 9: }
\titleformat{\section}
  {\normalfont\Large\bfseries}
  {Chapter \thesection:}
  {0.5em}
  {}
% \titleformat{\section}{
%     \scshape\raggedright\large\bfseries
%     }{}{0em}{}[\color{black}\titlerule]
%     \titlespacing{\section}{0pt}{5pt}{5pt}

\setstretch{1.5}
\setlist[itemize]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlist[enumerate]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlength{\footnotesep}{15pt} 
\setlength{\skip\footins}{15pt} 
\setlength{\parskip}{5pt}

\begin{document}

{\centering
  {\scshape \textls[50]{\fontsize{25}{30}\selectfont Reza {\bfseries Aliasgari Renani}}} \\ 
  {\fontsize{10}{10}\selectfont 11/01/2026} $|$
  {\fontsize{10}{10}\selectfont Motivation Letter} $|$
  {\fontsize{10}{10}\selectfont University of Tartu} $|$
  {\fontsize{10}{10}\selectfont PhD (E-Sailors 11)} $|$
  {\fontsize{10}{10}\selectfont Triangulated Celestial Navigation (TCN)}
\par}
\vspace{-15pt}
\noindent\rule{\textwidth}{0.5pt}

\vspace{-5pt}

My research objective is to contribute to autonomous navigation for small spacecraft by implementing visual navigation algorithms on embedded platforms. The E-Sailor~11 doctoral project at the University of Tartu focuses on MCU- and FPGA-based execution of triangulated celestial navigation for ESTCube-LuNa, including real-time image processing and in-orbit validation. This focus closely matches my background in FPGA development, fixed-point DSP, and experimental system verification. I am completing the final year of my Master's degree in Plasma Physics at Moscow Institute of Physics and Technology, and my experience with mission-relevant hardware and data pipelines has led me to pursue doctoral research in embedded space navigation.

I joined Dr.\ Koveshnikov's laboratory in the Russian Academy of Sciences over two years ago to study irradiated semiconductor devices. We investigated the effects of electron and gamma irradiation and hydrogen plasma treatments on \ce{SiO2}-based MOS devices, distinguishing trap contributions by location (oxide, semiconductor, interface) and carrier type (electrons, holes) using electrical characterization techniques. This work resulted in a first-author publication\footnote{R.~Aliasgari~Renani, O.A.~Soltanovich, M.A.~Knyazev, S.V.~Koveshnikov, ``Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by C--V and TSC techniques,'' \textit{Russian Microelectronics}, 2023, DOI: \href{https://doi.org/10.1134/S1063739723600516}{10.1134/S1063739723600516}} and strengthened my understanding of device stability under bias stress and radiation. I also developed optimized MATLAB automation programs for experimental techniques such as TSC, C--V, I--V, I--T, and DLTS measurements, which enabled systematic data acquisition and reduced experimental run-times.

After my undergraduate degree, I joined the System-on-Chip Development Laboratory under the supervision of Dr.\ Vasiliev to develop FPGA-based systems. I implemented video-processing algorithms in Verilog using both manual coding and HDL generated from Simulink models, built verification testbenches, and used Python for quality control. For these pipelines, I developed a fixed-point arithmetic library and LUT-based function approximations to support efficient DSP. I synthesized the designs, evaluated resource utilization (LUTs and BRAM), and validated them on a Xilinx Zybo Z7 platform with live camera input and HDMI output. The codebase was maintained under Git-based source control. Concurrently, at the Laboratory of Plasma Systems, I conducted research on radiation and plasma effects on FPGA devices. We exposed an FPGA board to 25--60~keV electron beams in low-pressure oxygen, generating plasma and X-rays from a tungsten target, while applying thermal cycling. The FPGA output signal was continuously monitored, and preliminary functionality tests were performed during and after exposure.

I have also worked on engineering projects\footnote{Project repositories: \href{https://github.com/icarus-imperium/rocket-2025}{Model Rocket (Icarus Imperium)}, \href{https://github.com/rezaaliasgarirenani/Rover}{Model Lunar Rover}, \href{https://github.com/rezaaliasgarirenani/Aircraft-Detection-System}{Aircraft Detection System}, \href{https://github.com/rezaaliasgarirenani/Non-Conservative-Electric-Fields-and-Voltmeters}{Non-Conservative Electric Fields and Voltmeters}} both independently and in team settings. In group projects, I built model rockets (40 and 60~N$\cdot$s impulse) and completed multiple launches, and I collaborated on a model lunar rover through several prototypes. I developed an aircraft detection system using photoresistors and transistor circuits with rotational and translational tracking. In an individual electronics experiment on non-conservative electric fields, I designed the setup, collected data, and documented how voltmeter readings become path-dependent under a time-varying magnetic flux. I also designed a CubeSat deployer and vibration fixture and validated prototypes through vibration testing.

In E-Sailor~11, I want to turn the project goals into a concrete onboard pipeline: a simplified MCU-based lunar orbit propagator, an FPGA gateware chain for image classification and object position estimation, and the triangulation and Kalman filtering steps that close the loop on navigation. I also want to build the testbenches and verification flow so the FPGA output can be compared directly with the CPU reference pipeline from E-Sailor~12, and to run screen-in-the-loop experiments using the photorealistic datasets and HIL tools from E-Sailor~15. The work requires careful version control, documentation, and end-to-end validation, and that is the way I like to work.

This position continues the line of work I have followed so far--embedded hardware, real-time processing, and verification under mission constraints. I would like to pursue this research under the supervision of Dr.\ Aditya Savio Paul, with guidance from Prof.\ Mihkel Pajusalu, Dr.\ Andris Slavinskis, and Dr.\ Jaan Viru, and to contribute during the CrystalSpace secondment. The combination of the University of Tartu, Tartu Observatory, and Nanocraft SIA is an environment where I can grow into careful, mission-focused engineering work on flight-ready visual navigation for ESTCube-LuNa and beyond.


\end{document}
