\documentclass[a4paper,12pt]{article}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[flushmargin]{footmisc}
\usepackage{mathptmx} % Times-like
\usepackage[version=4]{mhchem}
\usepackage{tabularx}
\usepackage{makecell} % for multiline table cells
\usepackage{booktabs} % For cleaner table rules
\usepackage[
  a4paper,
  top = 1.70cm,
  bottom = 1.70cm,
  left = 1.70cm,
  right = 1.70cm
]{geometry}
\renewcommand{\baselinestretch}{1.3}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{30pt}
\setlength{\skip\footins}{20pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    urlcolor=RoyalBlue,
    citecolor=RoyalBlue,
    anchorcolor=RoyalBlue
}
\urlstyle{same}
%\input{glyphtounicode} % comment out if you don't have this file
\newcolumntype{Y}{>{\centering\arraybackslash}X} % Centered X columns

\begin{document}

\begin{center}
    {\Huge \scshape {\fontsize{25}{30}\selectfont Reza} {\fontsize{25}{30}\selectfont\textbf{Aliasgari Renani}}} \\[3pt]
    {\small 10/10/2025} $|$
    {\small Additional Information} $|$
    {\small Experimental Physics} $|$
    {\small Technische Universität Dortmund} $|$
    {\small PhD}
    \vspace{-10pt}
\end{center}
\vspace{-10pt}
\noindent\rule{\textwidth}{0.5pt}

\vspace{10pt}

\textbf{Earliest Starting Date}\\
My Master's program at MIPT is scheduled to conclude on June 30, 2026, at which point I would be available to begin full-time. That said, I have already completed most of the required coursework and research, so I am able to dedicate significant time to the PhD project at TU Dortmund well before then. If the visa process allows for an earlier start, I would be happy to bridge the gap with a hybrid setup to continue my remaining commitments at MIPT remotely while joining Dr. Glaser's group in person as soon as possible. Otherwise, I am eager to dive into the hardware development and algorithms remotely right away, transitioning to on-site work the moment I finish my Master's degree and arrive in Dortmund.

\vspace{20pt}

\textbf{References}\\
Below is the contact information for three references who can speak to my qualifications and experience.

\vspace{10pt}

\small
\centering
{\renewcommand{\arraystretch}{2}%
\begin{tabularx}{\textwidth}{@{}YYYYY@{}}
\toprule
\textbf{Name} & \textbf{Position} & \textbf{Institution} & \textbf{Relationship} & \textbf{Contacts} \\
\midrule
Dr. Sergey Negodyaev & Dean of the Phystech School of Aerospace Technology & Moscow Institute of Physics and Technology & Academic Dean and Research Advisor & \makecell[c]{astech@mipt.ru \\ +7 495 408-53-44} \\

Dr. Chesnokov &  Dean of the Phystech-School of Radio Engineering and Computer Technology & Moscow Institute of Physics and Technology & Department Head and Mentor & \makecell[c]{astech@mipt.ru \\ +7 495 408-53-44} \\

Dr. Mikhail Vasiliev & Head of the Laboratory of Plasma Systems & Moscow Institute of Physics and Technology & Scientific Supervisor & \makecell[c]{vasilev.mn@mipt.ru \\ +7 916 550-18-07} \\
\bottomrule
\end{tabularx}}

\end{document}