
\documentclass[a4paper,11pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[version=4]{mhchem}
\usepackage[dvipsnames]{xcolor}
\usepackage[backend=biber,style=ieee]{biblatex}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{footmisc}
\usepackage{csquotes}
\usepackage{fontawesome5}
\usepackage[
  a4paper,
  top        = 2.00cm,
  bottom     = 2.00cm,
  left       = 2.00cm,
  right      = 2.00cm,
  headheight = 15pt,
  headsep    = 5pt,
  footskip   = 15pt
]{geometry}

\newcommand{\degreeawardvalue}{}
\newcommand{\universityvalue}{}
\newcommand{\addressvalue}{}
\newcommand{\unilogovalue}{}
\newcommand{\copyyearvalue}{}
\newcommand{\defenddatevalue}{}
\newcommand{\orcidvalue}{}
\newcommand{\rightsstatementvalue}{}
\newcommand{\degreeaward}[1]{\def\degreeawardvalue{#1}}
\newcommand{\university}[1]{\def\universityvalue{#1}}
\newcommand{\address}[1]{\def\addressvalue{#1}}
\newcommand{\unilogo}[1]{\def\unilogovalue{#1}}
\newcommand{\copyyear}[1]{\def\copyyearvalue{#1}}
\newcommand{\defenddate}[1]{\def\defenddatevalue{#1}}
\newcommand{\orcid}[1]{\def\orcidvalue{#1}}
\newcommand{\rightsstatement}[1]{\def\rightsstatementvalue{#1}}
\newcommand{\titleskip}{\vskip 4\bigskipamount}
\newcommand{\authorskip}{\vskip 2\bigskipamount}
\newcommand{\resumesection}[2]{\section{\textcolor{red}{#1}#2}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeItem}[1]{
    \item\small{#1}
}
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \small#3 & \small #4
    \end{tabular*}
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsecpresnum}{Chapter~}
\renewcommand{\cftsecaftersnum}{:}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\pagestyle{fancy}
\fancyhf{}
% \fancyfoot[R]{\thepage}
\urlstyle{same}
\addbibresource{references.bib}
\hypersetup{
  colorlinks=true,
  linkcolor=RoyalBlue,
  urlcolor=RoyalBlue,
  citecolor=RoyalBlue,
  anchorcolor=RoyalBlue
}
\settowidth{\cftsecnumwidth}{Chapter 9: }
% \titleformat{\section}
%   {\normalfont\Large\bfseries}
%   {Chapter \thesection:}
%   {0.5em}
%   {}
\titleformat{\section}{
    \scshape\raggedright\large\bfseries
    }{}{0em}{}[\color{black}\titlerule]
    \titlespacing{\section}{0pt}{5pt}{5pt}

\setstretch{1}
\setlist[itemize]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlist[enumerate]{topsep=4pt, itemsep=3pt, parsep=0pt, partopsep=0pt, leftmargin=*}
\setlength{\footnotesep}{15pt} 
\setlength{\skip\footins}{15pt} 
\setlength{\parskip}{0pt}

\begin{document}

%---------- HEADING ----------
{\centering
    {\scshape \textls[50]{\fontsize{25}{30}\selectfont Reza {\bfseries Aliasgari Renani}}} \\
    \vspace{5pt}
    \small ~ 
    \href{mailto:rezaaliasgarirenani@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{rezaaliasgarirenani@gmail.com}} $|$ ~
    \href{https://orcid.org/0009-0000-8983-755X}{\raisebox{-0.2\height}\faOrcid\ \underline{ORCID}} $|$ ~
    \href{https://www.researchgate.net/profile/Reza-Aliasgari-Renani}{\raisebox{-0.2\height}\faResearchgate\ \underline{ResearchGate}} $|$ ~
    \href{https://scholar.google.com/citations?user=L9Vv3C8AAAAJ&hl=en}{\raisebox{-0.2\height}\faGraduationCap\ \underline{Google Scholar}} $|$ ~
    \href{https://github.com/rezaaliasgarirenani}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} $|$ ~
    \href{https://linkedin.com/in/reza-aliasgari-renani}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}
\par}

{\setlength{\tabcolsep}{0pt}
%----------- EDUCATION -----------
\resumesection{Ed}{ucation}

\resumeSubHeadingListStart
    \resumeSubheading
        {\href{https://mipt.ru/}{Moscow Institute of Physics and Technology (MIPT, Phystech)}}{Sep 2024 -- Jun 2026}
        {\textbf{M.Sc.} in Applied Mathematics and Physics, Plasma Physics, GPA: 4.76/5.0}{Moscow, Russian Federation}
        {\resumeItem{\textbf{Thesis title:} Investigation of radiation-induced effects on programmable microelectronic systems by means of plasma-based facilities simulating space flight conditions.}}
    \resumeSubheading
        {\href{https://mipt.ru/}{Moscow Institute of Physics and Technology (MIPT, Phystech)}}{Sep 2020 -- Jun 2024}
        {\textbf{B.Sc.} in Technical Physics, Aerospace Technology, GPA: 4.53/5.0}{Moscow, Russian Federation}
        {\resumeItem{\textbf{Thesis title:} Investigation of the effects of low energy (1 - 20 keV) electrons and high energy (1 MeV) gamma quanta irradiation on the electro-physical properties of dielectric-semiconductor structures.}}
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\resumesection{Re}{search Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {\href{http://ai.mipt.ru/design-center}{\parbox[t]{\dimexpr\linewidth-6cm}{Design Center for the Development of Microprocessor Technology for AI Systems, System-on-Chip Development Laboratory}}}
        {Sep 2024 -- Present}
        {\textbf{Programmer / RTL Design Engineer}}{Moscow, Russian Federation}
        \resumeItemListStart
            \resumeItem{\textbf{DSP Implementation} \\ Ported mathematical algorithms into efficient Verilog implementations. Built a fixed-point library and LUT-based function approximations (Horner’s method) to support fixed-point computations. Implemented image processing algorithms (rgb2hsv, color segmentation, Sobel edge detection, global tone-mapping, demosaicing, bird’s-eye view, fisheye correction, image resizer) via Simulink HDL code generation and manually written Verilog. Optimized latency and throughput, resolved synchronization and pipelining issues.}
            \resumeItem{\textbf{Simulation, Verification and Synthesis} \\ Created comprehensive testbenches in Verilog and used Python for simulation automation and data analysis to verify DSP functionality and performance. Synthesized, mapped, and routed HDL code using Vivado (Xilinx Zybo Z7). Verified ISP algorithms by first streaming test images via HDMI from a host computer, and subsequently with a live camera connected to the FPGA.}
           \resumeItem{\textbf{Investigation of FPGA devices under electron-beam plasma exposure} \\ Conducted irradiation experiments on FPGA boards using electron beams (25 -- 60\,keV, up to 100\,mA) in low-pressure oxygen atmospheres ($10^{-6}$ -- 50\,Torr), generating plasma and X-rays. Applied combined thermal cycling ($218$--$393$\,K) and surface charging to evaluate FPGA reliability under radiation- and plasma-induced stress.}
        \resumeItemListEnd
    \resumeSubheading
        {\href{https://new.ras.ru/en/}{Institute of Microelectronics Technology, Russian Academy of Sciences}}{Mar 2023 -- Aug 2024}
        {\textbf{Laboratory Researcher}}{Moscow, Russian Federation}
        \resumeItemListStart
            \resumeItem{\textbf{Experimental Equipment Installation and Automation} \\ Installed experimental devices including Everbeing Cryo-station (80K – 450K) with 4 micromanipulators, Lakeshore Temperature Controller Model 336, Keithley SourceMeter 2450, Parametric Analyzer Keithley 4200A-SCS, Keysight Electrometer B2987A, Aktakom 3048, and Zurich Instruments MFIA Impedance Analyzer. Developed {\href{https://github.com/rezaaliasgarirenani/IMT-Automation}{applications}} in MATLAB to automate experimental techniques: Thermally Stimulated Current, Capacitance-Voltage, Current-Voltage, Current-Time and Deep-Level Transient Spectroscopy.}
            \resumeItem{\textbf{Theoretical Investigation} \\ Developed theoretical understanding and studied experimental techniques for semiconductor devices (MOS, MOSFET, diode, RRAM). Predicted sample behavior, and determined measurement parameters.}
            \resumeItem{\textbf{Experimental Investigation and Data Processing} \\ Conducted electrical characterization experiments on microelectronic structures, processed data using MATLAB and Origin Pro, removed extraneous random telegraph noise points, and compared results with theoretical models.}
        \resumeItemListEnd
    \resumeSubheading
        {\href{https://mipt.ru/dasr/about/kaf_faculty/mmsp}{Laboratory of Modeling of Mechanical Systems and Processes}}{Mar 2023 -- Aug 2024}
        {\textbf{Engineer / Technician}}{Moscow, Russian Federation}
        \resumeItemListStart
            \resumeItem{\textbf{Engineering Design and Development} \\ Designed models for a CubeSat orbital deployer and vibration fixture in SolidWorks. Prototypes passed random vibration simulation and dynamic analysis, and were tested on a UVE vibro-stand for mechanical factors.}
        \resumeItemListEnd
\resumeSubHeadingListEnd
}

%----------- PUBLICATIONS ---------------
\resumesection{Pu}{blications \& Conferences}
\resumeSubHeadingListStart
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by capacitance-voltage and thermally stimulated current techniques. \href{https://doi.org/10.1134/S1063739723600516}{Journal Paper}, \textit{Russian Microelectronics}, 2023
    \vspace{2pt}
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ Study of \ce{SiO2} based MOS by capacitance-voltage and thermally stimulated current techniques. \href{https://icmne.ftian.ru/wp-content/uploads/icmne-2023_e-version.pdf}{Presentation}, p.122. \textit{The 15th International Conference Micro- And Nanoelectronics} (\href{https://icmne.ftian.ru}{ICMNE 2023})
    \vspace{2pt}
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ Investigation of electrically active defects introduced into silicon oxide by irradiation of low-energy electrons, by methods of Capacitance-Voltage characteristics and thermally-stimulated current. \href{https://cebt23.iptm.ru/download/numbered/91.pdf}{Poster}, \textit{Second Joint Conference on Electron Beam Technologies and X-ray Optics in Microelectronics} (\href{https://cebt23.iptm.ru}{CALT 2023})
    \vspace{2pt}
    \item \underline{V. Vologin}, R. Aliasgari Renani, V. Vasilevskiy, V. Chesnokov. \\ Comparative analysis of manual and Simulink-generated Verilog code for image processing algorithms. Presentation, \textit{\href{https://meetups.yadro.com/fpga-msk-1125/}{FPGA-Systems Conference 2025}}
\resumeSubHeadingListEnd

%----------- TECHNICAL SKILLS -----------
\resumesection{Te}{chnical Skills}
{\centering
    \begin{minipage}[t]{0.45\textwidth}
        \textbf{Advanced}
        \begin{itemize}
            \item Automation of Experimental Techniques
            \item Electrical Characterization
            \item Data Processing, LaTeX
            \item MATLAB, Simulink, HDL Coder
            \item Verilog, RTL Design
            \item FPGA Development
            \item Fixed-Point Computations
            \item SciPy, Cocotb, OpenCV
        \end{itemize}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.45\textwidth}
        \textbf{Intermediate}
        \begin{itemize}
            \item Python, C++, Arduino
            \item Vivado, Vitis
            \item Git, Unix/Linux OS
            \item OriginLab
            \item SolidWorks
            \item ERDAS IMAGINE
            \item PCB, EasyEDA
            \item OpenRocket
        \end{itemize}
    \end{minipage}
\par}

%----------- PROJECTS -----------
\resumesection{Pr}{ojects}
    \noindent {\href{https://github.com/icarus-imperium/rocket-2025}{\textbf{Model Rocket}}} \hfill \textbf{Apr 2023 and 2025}
    \begin{itemize}
    \item Constructed model rockets with 40 and 60 Newton-second impulses as part of a team.
    \item Launched three model rockets over two years at the Cosmonautics Day of MIPT.
    \end{itemize}
    {\href{https://github.com/rezaaliasgarirenani/Rover}{\textbf{Model Lunar Rover}}} \hfill \textbf{Jun 2023}
    \begin{itemize}
    \item Collaborated on a machine capable of navigating obstacles without round wheels.
    \item Tested multiple prototypes, with the final design approved by the laboratory head.
    \end{itemize}
    {\href{https://github.com/rezaaliasgarirenani/Aircraft-Detection-System}{\textbf{Aircraft Detection System}}} \hfill \textbf{Jun 2022}
    \begin{itemize}
    \item Investigated and applied algorithms to detect aircraft using photoresistors and transistors.
    \item Developed a system capable of rotational and translational movement to track aircraft.
    \end{itemize}
    {\href{https://github.com/rezaaliasgarirenani/Non-Conservative-Electric-Fields-and-Voltmeters}{\textbf{Investigation of Non-Conservative Electric Fields and Voltmeters}}} \hfill \textbf{May 2022}
    \begin{itemize}
    \item Designed an experimental setup to analyze position-dependency of voltmeter readings in parallel circuits.
    \item Demonstrated the non-intuitive potential differences generated by changing magnetic fields.
    \end{itemize}

%----------- AWARDS -----------
\resumesection{Aw}{ards}
\begin{itemize}
    \item{\textbf{Recipient:} Full State Russian Scholarship for Foreign Students, MIPT} \hfill \textbf{Sep 2024}
    \item{\textbf{Recipient:} Iranian State Scholarship, Isfahan University of Technology} \hfill \textbf{Sep 2019}
    \item{\textbf{Awardee:} Participant of the \href{https://congress.aero/en/}{5th and 7th Eurasian Aerospace Congress}} \hfill \textbf{Jul 2023 and 2025}
\end{itemize}

%----------- LANGUAGES -----------
\resumesection{La}{nguages}
{\centering
    \textbf{English}: C2 (TOEFL iBT 113) \quad $|$ \quad 
    \textbf{Russian}: B1 \quad $|$ \quad 
    \textbf{German}: B1 (ÖSD) \quad $|$ \quad 
    \textbf{Farsi}: Native
\par}

\end{document}
