
\documentclass[a4paper,12pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage{mathptmx}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[version=4]{mhchem}
\usepackage[usenames,dvipsnames]{color}
\usepackage[
a4paper,
top = 2.00cm,
bottom = 2.00cm,
left = 1.70cm,
right = 1.70cm
]{geometry}

\renewcommand{\baselinestretch}{1.5}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

\hypersetup{
colorlinks=true,
linkcolor=RoyalBlue,
urlcolor=RoyalBlue,
citecolor=RoyalBlue,
anchorcolor=RoyalBlue
}

\urlstyle{same}
\pagestyle{fancy}
\fancyhf{}
% \fancyfoot[R]{\thepage}

\begin{document}

\begin{center}
    {\Huge \scshape {\fontsize{25}{30}\selectfont{Reza}} {\fontsize{25}{30}\selectfont{\textbf{Aliasgari Renani}}}} \\ \vspace{3pt}
    {\small {07/12/2025}} $|$
    {\small {Additional Information}} $|$
    {\small {Hamburg U., Heidelberg U., Munich U., RWTH Aachen U.}} $|$
    {\small {PhD Position}} \\
    {\small {Foundation Models in Astrophysics and Particle Physics}}
    \vspace{-10pt}
\end{center}
\vspace{-10pt}
\noindent\rule{\textwidth}{0.5pt}

\vspace{10pt}

\textbf{Earliest Starting Date}\\
My Master's program at MIPT is scheduled to conclude on June 30, 2026, at which point I would be available to begin full-time. That said, I have already completed most of the required coursework and research, so I am able to dedicate significant time to the PhD project for Foundation Models in Astrophysics and Particle Physics before then. If the visa process allows for an earlier start, I would be happy to bridge the gap with a hybrid setup to continue my remaining commitments at MIPT remotely while joining Dr. Mertsch's group in person as soon as possible. Otherwise, I am eager to dive into the hardware development and algorithms remotely right away, transitioning to on-site work the moment I finish my Master's degree and arrive at RWTH Aachen, or another university for this project if needed.

\vspace{20pt}

\textbf{References}\\
Below is the contact information for three references who can speak to my qualifications and experience.

\vspace{10pt}

\small
\centering
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{@{}YYYYY@{}}
\toprule
\textbf{Name} & \textbf{Position} & \textbf{Institution} & \textbf{Relationship} & \textbf{Contacts} \\
\midrule
Dr. Sergey Negodyaev & Dean of the Phystech School of Aerospace Technology & Moscow Institute of Physics and Technology & Academic Dean and Research Advisor & \makecell[c]{astech@mipt.ru \\ +7 495 408-53-44} \\

Dr. Yakov Lvovich &  Head of the System-on-Chip Development Laboratory & Moscow Institute of Physics and Technology & Department Head and Mentor & \makecell[c]{frkt@mipt.ru \\ +7 495 408-54-90} \\

Dr. Mikhail Vasiliev & Head of the Laboratory of Plasma Systems & Moscow Institute of Physics and Technology & Scientific Supervisor & \makecell[c]{vasilev.mn@mipt.ru \\ +7 916 550-18-07} \\
\bottomrule
\end{tabularx}}

\end{document}