%-------------------------
% Resume in Latex
% Author: Reza Aliasgari Renani (reordered to reverse-chronological)
% License: MIT
%------------------------

\documentclass[a4paper, 11pt]{article}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[version=4]{mhchem}
\usepackage[
  a4paper,
  top    = 1.70cm,
  bottom = 1.70cm,
  left   = 1.70cm,
  right  = 1.70cm
]{geometry}
\usepackage{mathptmx} % Added for Times New Roman-like font

\renewcommand{\baselinestretch}{1.1}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Defining custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \small#3 & \small #4
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    urlcolor=RoyalBlue,
    citecolor=RoyalBlue,
    anchorcolor=RoyalBlue
}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{30pt} % Fixes \footskip warning
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Formatting section titles
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Starting the document
\begin{document}


%-----------PUBLICATIONS---------------
\section{{\textcolor{red}{Pu}blications} \& Conferences}
\resumeSubHeadingListStart
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ \textit{Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by capacitance-voltage and thermally stimulated current techniques.} \href{https://doi.org/10.1134/S1063739723600516}{Journal Paper}, Russian Microelectronics, 2023
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ \textit{Study of \ce{SiO2} based MOS by capacitance-voltage and thermally stimulated current techniques.} \href{https://icmne.ftian.ru/wp-content/uploads/icmne-2023_e-version.pdf}{Presentation}, p.122. The 15th International Conference Micro- And Nanoelectronics (\href{https://icmne.ftian.ru}{ICMNE 2023})
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ \textit{Investigation of electrically active defects introduced into silicon oxide by irradiation of low-energy electrons, by methods of Capacitance-Voltage characteristics and thermally-stimulated current.} \href{https://cebt23.iptm.ru/download/numbered/91.pdf}{Poster}, Second Joint Conference on Electron Beam Technologies and X-ray Optics in Microelectronics (\href{https://cebt23.iptm.ru}{CALT 2023})
    \item \underline{V. Vologin}, R. Aliasgari Renani, V. Vasilevskiy, V. Chesnokov \\ \textit{Comparative analysis of manual Verilog and Simulink-generated HDL code for image processing algorithms.} Forthcoming presentation, \href{https://meetups.yadro.com/fpga-msk-1125/}{FPGA-Systems Conference 2025}
    
\resumeSubHeadingListEnd
\vspace{-20pt}


\end{document}
