
\documentclass[a4paper,12pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage{mathptmx}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[version=4]{mhchem}
\usepackage[usenames,dvipsnames]{color}
\usepackage[
a4paper,
top = 2.00cm,
bottom = 2.00cm,
left = 1.70cm,
right = 1.70cm
]{geometry}



\renewcommand{\baselinestretch}{1.11}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\renewcommand{\arraystretch}{2}
\setlength{\heavyrulewidth}{\lightrulewidth}
\setlength{\aboverulesep}{0pt}
\setlength{\belowrulesep}{0pt}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\hypersetup{
colorlinks=true,
linkcolor=RoyalBlue,
urlcolor=RoyalBlue,
citecolor=RoyalBlue,
anchorcolor=RoyalBlue
}

\urlstyle{same}
\pagestyle{fancy}
\fancyhf{}
% \fancyfoot[R]{\thepage}

\begin{document}

\begin{center}
  {\Huge \scshape {\fontsize{25}{25}\selectfont{Reza}} {\fontsize{25}{25}\selectfont{\textbf{Aliasgari Renani}}}} \\ 
  \vspace{2pt}
  {\fontsize{10}{10}\selectfont 30/12/2025} $|$
  {\fontsize{10}{10}\selectfont Additional Information} $|$
  {\fontsize{10}{10}\selectfont Aalto University} $|$
  {\fontsize{10}{10}\selectfont PhD (E-Sailors 4)} $|$
  {\fontsize{10}{10}\selectfont Design and Engineering for Nanospacecraft}
\end{center}

\vspace{-20pt}
\noindent\rule{\textwidth}{0.5pt}


%-----------StartingDate---------------
\noindent \textbf{Earliest Starting Date}\\
My Master's program at MIPT is scheduled to conclude on June 30 2026, at which point I would be available to begin full-time upon my arrival at TUDelft.

\vspace{20pt}

\noindent \textbf{References}\\
Below is the contact information for three references who can speak to my qualifications and experience.
\vspace{2pt}

%-----------References---------------
\small
\centering
\begin{tabularx}{\textwidth}{@{}YYYYY@{}}
\toprule
\addlinespace[-5pt]
\textbf{Name} & \textbf{Position} & \textbf{Institution} & \textbf{Relationship} & \textbf{Contacts} \\
\midrule
Dr. Sergey Negodyaev & Dean of the Phystech School of Aerospace Technology & Moscow Institute of Physics and Technology & Academic Dean and Research Advisor & astech@mipt.ru\newline +7 495 408-53-44 \\

Dr. Yakov Lvovich &  Head of the System-on-Chip Development Laboratory & Moscow Institute of Physics and Technology & Department Head and Mentor & frkt@mipt.ru \newline +7 495 408-54-90 \\

Dr. Mikhail Vasiliev & Head of the Laboratory of Plasma Systems & Moscow Institute of Physics and Technology & Scientific Supervisor & vasilev.mn@mipt.ru \newline +7 916 550-18-0 \\
\bottomrule
\end{tabularx}
\par

%-----------Publications---------------
\vspace{20pt}
\section{{Publications} \& Conferences}
\resumeSubHeadingListStart
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ \textit{Investigation of low energy electron irradiated \ce{SiO2} based MOS devices by capacitance-voltage and thermally stimulated current techniques.} \href{https://doi.org/10.1134/S1063739723600516}{Journal Paper}, Russian Microelectronics, 2023
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ \textit{Study of \ce{SiO2} based MOS by capacitance-voltage and thermally stimulated current techniques.} \href{https://icmne.ftian.ru/wp-content/uploads/icmne-2023_e-version.pdf}{Presentation}, p.122. The 15th International Conference Micro- And Nanoelectronics (\href{https://icmne.ftian.ru}{ICMNE 2023})
    \item \underline{R. Aliasgari Renani}, O.A. Soltanovich, M.A. Knyazev, S.V. Koveshnikov. \\ \textit{Investigation of electrically active defects introduced into silicon oxide by irradiation of low-energy electrons, by methods of Capacitance-Voltage characteristics and thermally-stimulated current.} \href{https://cebt23.iptm.ru/download/numbered/91.pdf}{Poster}, Second Joint Conference on Electron Beam Technologies and X-ray Optics in Microelectronics (\href{https://cebt23.iptm.ru}{CALT 2023})
    \item \underline{V. Vologin}, R. Aliasgari Renani, V. Vasilevskiy, V. Chesnokov \\ \textit{Comparative analysis of manual and Simulink-generated Verilog code for image processing algorithms.} Presentation, \href{https://meetups.yadro.com/fpga-msk-1125/}{FPGA-Systems Conference 2025}
\resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}
